M.Sc. Proposal: \\ \bigskip Computational Electrokinetics

### 2013-01-11 notes/thesis-latex-template/thesis.tex
Update thesis.

\subsection{Ion-exchanger results}
For $\beta \ll 1$, the linear regime is dominant \eqref{eq:linear_velocity}.
When $\gamma \approx 1$, the cubic regime, where $\cU = O(\beta^3)$, 
dominates the linear one, even for weak electric fields. 
This phenomenon is confirmed both by the numerical
results and by asymptotic expansion of the nonlinear system (for $\alpha=0$).
The switch from the linear regime to the cubic regime occurs at 
an electric field value of $\beta = O(\sqrt{|\gamma - 1|})$.
The numerical results $\cU^h$, 
as well as the analytical ones \eqref{eq:cubic}, are given in Figure \ref{fig:IonExCubic}.
The numerical solver uses $N_r \times N_\theta = (400 \times 50)$, 
$R_{\max} = 10^7$ ($\Delta_r \approx 0.041$),
$K = 3$, $M = 5$ and $\beta = 10^{t}$ for $t = -2:0.1:0.5$.

@@

\subsection{Electrophoresis results}
In this scenario the linear regime is dominant \eqref{eq:linear_velocity}.
In order to verify the solver, the numerical steady-state velocity is compared to the
analytical solution \cite{schnitzer2012cubic}. Since the cubic correction is much smaller than
the linear solution for $\beta \ll 1$, the difference between numerical results and
the linear solution is compared to the cubic correction term.

@@

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.8\textwidth]{figs/Cubic/ionex_cubic1.eps}
    \includegraphics[width=0.8\textwidth]{figs/Cubic/ionex_cubic2.eps}
        \caption[Ion exchanger steady-state velocity]{
        Steady-state velocity $\cU$ as a function of the 
        electric field magnitude $\beta$, for $\gamma < 1$ (top) and $\gamma > 1$ (bottom). 
        The analytic cubic solution \eqref{eq:cubic} is represented by curves
        (solid for $\cU > 0$, dashed for $\cU < 0$), 
        and the numerical results are represented by markers 
        (circles for $\cU > 0$, squares for $\cU < 0$). Note that linear and
        cubic regimes match well the numerical results, including the critical $\beta$ 
        behaviour \eqref{eq:crit_beta}. 
        }
	    \label{fig:IonExCubic}
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/N1.eps}
	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/N2.eps}
	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/N5.eps}
	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/N10.eps}
        \caption[Ion exchanger streamlines -- numerical results]{
        Streamlines of the flow for various electric field $\beta$ values: 
        numerical results for $\gamma = 0.9$.  
        The steady-state velocity $\cU$ is positive, so the
        ion-exchanger drifts to the right. }
    \label{fig:Vortex1}
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/A1.eps}
	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/A2.eps}
	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/A5.eps}
	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/A10.eps}
        \caption[Ion exchanger streamlines -- analytical results]{
        Streamlines of the flow for various electric field $\beta$ values: 
        analytical approximation for $\gamma = 0.9$ (see Section \ref{sec:asymp}).
        The steady-state velocity $\cU$ is positive, so the
        ion-exchanger drifts to the right.}
    \label{fig:Vortex2}
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=1\textwidth]{figs/quadratic_order.eps}
        \caption[Quadratic convergence of steady-state velocity]{
        The discretization error between the numerical and analytical solutions for 
        $\alpha = 0$ ,$\Du = 0.5$, $\bar\zeta = 6$ and $R_{max} = 100$. The markers represent
        the discretization errors for various grid sizes, and the dotted lines correspond to linear
        functions of $\beta$, scaled by $4^n$. As mesh cell size decreases by 2, the discretization
        }
	    \label{fig:quadratic}
    \end{center}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Ion-exchanger results}
For $\beta \ll 1$, the linear regime \cite{yariv2010asymptotic} is dominant.
When $\gamma \approx 1$, the cubic regime, where $\cU = O(\beta^3)$, 
dominates the linear one, even for weak electric fields. 
This phenomenon is confirmed both by the numerical
results and by asymptotic expansion of the nonlinear system (for $\alpha=0$).
The switch from the linear regime to the cubic regime occurs at 
an electric field value of $\beta = O(\sqrt{|\gamma - 1|})$.
The numerical results $\cU^h$, 
as well as the analytical ones \eqref{eq:cubic}, are given in Figure \ref{fig:IonExCubic}.
The numerical solver uses $N_r \times N_\theta = (400 \times 50)$, 
$R_{\max} = 10^7$ ($\Delta_r \approx 0.041$),
$K = 3$, $M = 5$ and $\beta = 10^{t}$ for $t = -2:0.1:0.5$.

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.7\textwidth]{figs/Cubic/ionex_cubic1.eps}
    \includegraphics[width=0.7\textwidth]{figs/Cubic/ionex_cubic2.eps}
        \caption[Ion exchanger steady-state velocity]{
        Steady-state velocity $\cU$ as a function of the 
        electric field magnitude $\beta$, for $\gamma < 1$ (top) and $\gamma > 1$ (bottom). 
        The analytic cubic solution \eqref{eq:cubic} is represented by curves
        (solid for $\cU > 0$, dashed for $\cU < 0$), 
        and the numerical results are represented by markers 
        (circles for $\cU > 0$, squares for $\cU < 0$). Note that linear and
        cubic regimes match well the numerical results, including the critical $\beta$ 
        behaviour \eqref{eq:crit_beta}. 
        }
	    \label{fig:IonExCubic}
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/N1.eps}
	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/N2.eps}
	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/N5.eps}
	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/N10.eps}
        \caption[Ion exchanger streamlines -- numerical results]{
        Streamlines of the flow for various electric field $\beta$ values: 
        numerical results for $\gamma = 0.9$.  
        The steady-state velocity $\cU$ is positive, so the
        ion-exchanger drifts to the right. }
    \label{fig:Vortex1}
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/A1.eps}
	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/A2.eps}
	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/A5.eps}
	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/A10.eps}
        \caption[Ion exchanger streamlines -- analytical results]{
        Streamlines of the flow for various electric field $\beta$ values: 
        analytical approximation for $\gamma = 0.9$ (see Section \ref{sec:asymp}).
        The steady-state velocity $\cU$ is positive, so the
        ion-exchanger drifts to the right.}
    \label{fig:Vortex2}
    \end{center}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Electrophoresis results}
For $\beta \ll 1$, the linear regime \cite{schnitzer2012surface} is dominant.
In order to verify the solver, the numerical steady-state velocity is compared to the
analytical solution \cite{schnitzer2012cubic}, derived by Schnitzer and Yariv. 
Since the cubic correction is much smaller than
the linear solution for $\beta \ll 1$, the difference between numerical results and
the linear solution is compared to the cubic correction term.

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=1\textwidth]{figs/quadratic_order.eps}
        \caption[Quadratic convergence of steady-state velocity]{
        The discretization error between the numerical and analytical solutions for 
        $\alpha = 0$, $\Du = 0.5$, $\bar\zeta = 6$ and $R_{max} = 100$. The markers represent
        the discretization errors for various grid sizes, and the dotted lines correspond to linear
        functions of $\beta$, scaled by $4^n$. 
        The graph show that, as the number of grid points in each dimension increases by 2, 
        the discretization error decreases by 4.
        }
	    \label{fig:quadratic}
    \end{center}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Electrophoresis for large $\beta$ }
When the electric field is large, nonlinear effects dominate the solution.
In order to investigate the problem solution for strong electric fields, 
we have run the solver on the TAMNUN HPC cluster \cite{tamnun}.
Large grid sizes ($256 \times 256$ and $512 \times 512$)
are used to verify that the numerical solution converges when the grid becomes finer
and that no numerical artifacts are present in the solution.
Moreover, several $R_{max} \in \{10, 30, 100\}$ values are used, to make sure it
has no major impact on the solution.

The results are shown at the following figures. 
The steady-state velocity results are shown in Figure \ref{fig:LargeBetaV}. 
When $\beta$ becomes large, the salt concentration $C$ near the front of the particle approaches zero,
while creating a wake behind the particle.
This is results in high gradients in $\log C$ near the front of the particle 
(Figures \ref{fig:LargeBeta1a}, \ref{fig:LargeBeta1b} and \ref{fig:LargeBeta1c}) 
and, therefore, strong electric field $\bE$ form near the particle surface 
(Figures \ref{fig:LargeBeta2a}, \ref{fig:LargeBeta2b} and \ref{fig:LargeBeta2c})
due to effective boundary conditions at Eq. \ref{eq:ephor_bnd}. 
The streamline pattern doesn't change drastically for different electric field magnitudes, as shown in Figure \ref{fig:LargeBeta3}.

It appears that a boundary layer starts to form around the front of the particle for strong
electric fields. This causes numerical problems to the current solver -- yielding a convergence
problems for $\beta > 5$. The convergence problems start earlier
for smaller grid size, and for higher $R_{max}$ values, probably
due to insufficient resolution at the $\brhat$ direction near
the particle surface.

\begin{figure}
    \begin{center}
    \includegraphics[width=1\textwidth]{figs/LargeBetaV.eps}
        \caption{Large $\beta$ results for $\cU$ ($\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$).}
	    \label{fig:LargeBetaV}	    
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
        \caption{Large $\beta$ results for $C$: grid size $128 \times 128$, 
        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.}
	    \label{fig:LargeBeta1a}	    
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
        \caption{Large $\beta$ results for $C$: grid size $256 \times 256$, 
        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.}
	    \label{fig:LargeBeta1b}	    
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
        \caption{Large $\beta$ results for $C$: grid size $512 \times 512$, 
        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.}
	    \label{fig:LargeBeta1c}	    
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
        \caption{Large $\beta$ results for $\varPhi$:
        grid size $128 \times 128$, $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.}
	    \label{fig:LargeBeta2a}	    
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
        \caption{Large $\beta$ results for $\varPhi$:
        grid size $256 \times 256$, $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.}
	    \label{fig:LargeBeta2b}	    
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
        \caption{Large $\beta$ results for $\varPhi$:
        grid size $512 \times 512$, $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.}
	    \label{fig:LargeBeta2c}	    
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
        \caption{Large $\beta$ streamlines results: grid size $512 \times 512$, 
        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.}
	    \label{fig:LargeBeta3}	    
    \end{center}
\end{figure}

@@
